master thesis

### 2017-10-02 Masterarbeit - Latex/Masterarbeit - Lydia Buntrock - v2.tex
add some literature
Former-commit-id: 0e68df5887343952082ce0c71c6b27525e68abba

  %--------------------------------------------------------------------------------------------------- 
  \section{Definitions}
    \begin{definition} parsimony \cite{Cunningham1998}
    \end{definition}
    \begin{definition} taxonomy \\
      Taxonomic tree – Taxonomy is the classification, identification and naming of organisms. It is 
        usually richly informed by phylogenetics, but remains a methodologically and logically 
        distinct discipline. The Taxonomic levels are Kingdom, Phylum, Class, Order, Family, Genus, 
        Species and maybe some superclasses between them. \\
      coarser classification \\
      In each level the nodes can have more than 2 children
    \end{definition}
    \begin{definition} phylogeny \\
      Phylogenetic tree – Phylogenetics is the study of evolutionary history and the relationships 
        among individuals or groups of organisms. The result ot these analysis is a  phylogeny or 
        phylogenetic tree. The phylogenetic tree is a hypothesis about the history of the evolutionary 
        relationships of a group of organisms. \\
      A perfect tree would be binary \\
      no levels only time
    \end{definition}
    \begin{definition} parasite \\
      Parasitism – Parasitism is an interaction relationship between two organisms living together in 
        more or less intimate association in a relationship in which association is disadvantageous or 
        destructive to one of the organisms. \\
      http://www.ebi.ac.uk/QuickGO/term/GO:0072519 \\
      ontology definition of the interaction 'is parasite of' from GloBI the database we use here. \\
      exist very different types of parasites: endoparasites, broodparasitism, ... \\
      40\% of species are parasites, but the most of them are understudied. \cite{Windsor1998}

@@

  %--------------------------------------------------------------------------------------------------- 
  \section{Motivation}
    study parasites:
    \begin{itemize}
      \item für jedes Ökosystem unentbehrlich [Marius]
      \item Wechselwirkungen in 75\% der Verbindungen in den Nahrungsmittelbahnen [Marius]
      \item agglomerieren Schadstoffe, binden 30 bis 50\% der Schadstoffmasse innerhalb eines Ökosystem [Marius]
      \item Dezimierung der Bevölkerung der störenden Arten [Marius]
    \end{itemize}
    big data:
    \begin{itemize}
      \item data accumulates faster than ever. Biological data is no exception but scientists still struggle to harvest this rapidly growing pile of databases. [Marius]      
    \end{itemize}
    origins of parasitism: \\
    Many studies tried to find the origins of parasitism. For example in Nematodes [14, 29], in Lice 
      [28], in Plathylminthes [30, 31] and in Metazoa in general [32, 33, 1] scientists searched for 
      these origins. The most recent analysis is the one from Sara Weinstein and Armand M. Kuris. 
      They came to the conclusion that parasitism evolved at least 223 times indepedently in the 
      kingdom of Animalia. They found most of the origins inside the phylum Arthropoda [1]. [Marius] \\
    Wenn wir die Ursprünge des Parasitums verstehen können, können wir die Evolution von Pathogenen 
      vorhersagen und welche genetischen Anpassungen für eine Transition vom freien Leben zu einem 
      parasitären Lebensstil notwendig sind [21]. Es könnte sogar zu einem Punkt führen, an dem wir 
      die Immunität gegen Antibiotika von Pathogenen vorhersagen konnten. [Marius]

>>>>

  %--------------------------------------------------------------------------------------------------- 
  \section{Definitions}
    \begin{definition} parsimony \cite{Cunningham1998}
    \end{definition}
    \begin{definition} taxonomy \\
      Taxonomic tree – Taxonomy is the classification, identification and naming of organisms. It is 
        usually richly informed by phylogenetics, but remains a methodologically and logically 
        distinct discipline. The Taxonomic levels are Kingdom, Phylum, Class, Order, Family, Genus, 
        Species and maybe some superclasses between them. \\
      coarser classification \\
      In each level the nodes can have more than 2 children
    \end{definition}
    \begin{definition} phylogeny \\
      Phylogenetic tree – Phylogenetics is the study of evolutionary history and the relationships 
        among individuals or groups of organisms. The result ot these analysis is a  phylogeny or 
        phylogenetic tree. The phylogenetic tree is a hypothesis about the history of the evolutionary 
        relationships of a group of organisms. \\
      A perfect tree would be binary \\
      no levels only time
      \todo{synthesis tree} \cite{Hinchliff2015}
    \end{definition}
    \begin{definition} parasite \\
      Parasitism – Parasitism is an interaction relationship between two organisms living together in 
        more or less intimate association in a relationship in which association is disadvantageous or 
        destructive to one of the organisms. \\
      http://www.ebi.ac.uk/QuickGO/term/GO:0072519 \\
      ontology definition of the interaction 'is parasite of' from GloBI \cite{Poelen2014} the database we use here. \\
      exist very different types of parasites: endoparasites, broodparasitism, ... \\
      40\% of species are parasites, but the most of them are understudied. \cite{Windsor1998}

@@

  %--------------------------------------------------------------------------------------------------- 
  \section{Motivation}
    Weinstein und Kuris Paper \cite{Weinstein2016} \\
    study parasites:
    \begin{itemize}
      \item für jedes Ökosystem unentbehrlich [Marius]
      \item Wechselwirkungen in 75\% der Verbindungen in den Nahrungsmittelbahnen [Marius]
      \item agglomerieren Schadstoffe, binden 30 bis 50\% der Schadstoffmasse innerhalb eines Ökosystem [Marius]
      \item Dezimierung der Bevölkerung der störenden Arten [Marius]
    \end{itemize}
    big data:
    \begin{itemize}
      \item data accumulates faster than ever. Biological data is no exception but scientists still struggle to harvest this rapidly growing pile of databases. [Marius]      
    \end{itemize}
    origins of parasitism: \\
    Many studies tried to find the origins of parasitism. For example in Nematodes [14, 29], in Lice 
      [28], in Plathylminthes [30, 31] and in Metazoa in general [32, 33, 1] scientists searched for 
      these origins. The most recent analysis is the one from Sara Weinstein and Armand M. Kuris. 
      They came to the conclusion that parasitism evolved at least 223 times indepedently in the 
      kingdom of Animalia. They found most of the origins inside the phylum Arthropoda [1]. [Marius] \\
    Wenn wir die Ursprünge des Parasitums verstehen können, können wir die Evolution von Pathogenen 
      vorhersagen und welche genetischen Anpassungen für eine Transition vom freien Leben zu einem 
      parasitären Lebensstil notwendig sind [21]. Es könnte sogar zu einem Punkt führen, an dem wir 
      die Immunität gegen Antibiotika von Pathogenen vorhersagen konnten. [Marius]
